Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-20 paper/structureScene.tex
Edit intro

To design better representations for the similarity retrieval task, we draw inspiration from a closely related, and more mature, field of investigation: the classification of acoustic scenes.This task, consisting of predicting scene labels from audio recordings, is narrower in its range of applications, but has the advantage of being rooted in the cognitive psychology of categorization \cite{dubois2006cognitive,guastavino_ideal_2006}. In addition, it has received significant attention from the data mining community for some time, resulting in the availability of well-designed datasets and competitive algorithms for solving it.

Adressing this task requires first to be able to capture meanningful aspects within the signal at a small time scale. In other words, how do we represent an extract of the auditory scene signal over a sub-second interval? A standard tool for this are the mel-frequency cepstral coefficients (MFCCs), originally developed for speech processing \cite{davis-mermelstein}, but which have found wider use in recent years in music information retrieval \cite{logan} and environemental audio processing \cite{aucouturier2007bag}. A richer set of features are found in the scattering transform, a generic signal representation which has enjoyed significant success in various audio classification tasks \cite{Anden2014}.

>>>>

To design better representations for the similarity retrieval task, we draw inspiration from a closely related, and more mature, field of investigation: the classification of acoustic scenes. This task, consisting of predicting scene labels from audio recordings, is narrower in its range of applications, but has the advantage of being rooted in the cognitive psychology of categorization \cite{dubois2006cognitive,guastavino_ideal_2006}. In addition, it has received significant attention from the data mining community for some time, resulting in the availability of well-designed datasets and competitive algorithms for solving it.

Adressing this task requires first to be able to capture meaningful aspects within the signal at small time scales. In other words, how do we represent an extract of the auditory scene signal over a sub-second interval? A standard tool for this are the mel-frequency cepstral coefficients (MFCCs), originally developed for speech processing \cite{davis-mermelstein}, but which have found wider use in recent years in music information retrieval \cite{logan} and environmental audio processing \cite{aucouturier2007bag}. A richer set of features are found in the scattering transform, a generic signal representation which has enjoyed significant success in various audio classification tasks \cite{Anden2014}.
